### 2016-05-12 tikz/moveex.tex
slides "done"

  \draw[edge] (0) to node[very near start, above] {0} node[very near end, above] {1} (1);
  \draw[edge] (1) to node[very near start, below] {0} node[very near end, above] {1} (2);
  \draw[edge,bend right] (2.north west) to node[very near start, right] {0} node[very near end, above] {2} (0);
  \draw[edge] (0) to node[very near start, right] {1} node[very near end, left ] {0} (3);
  \draw[edge] (3) to node[very near start, above] {1} node[very near end, below] {1} (4);
  \draw[edge] (4) to node[very near start, below] {0} node[very near end, below] {1} (5);
  \draw[edge] (5) to node[very near start, above] {0} node[very near end, below] {2} (1);
  \draw[edge] (1) to node[very near start, left ] {3} node[very near end, left ] {2} (6);
  \draw[edge] (6) to node[very near start, above] {0} node[very near end, above] {1} (7);
  \draw[edge] (8) to node[very near start, above] {0} node[very near end, right] {0} (7);
  \draw[edge] (8) to node[very near start, above] {1} node[very near end, right] {2} (5);
  \draw[edge] (9) to node[very near start, below] {1} node[very near end, below] {3} (5);
  \draw[edge,bend right=20] (9) to node[very near start, below] {0} node[very near end, below] {1} (6);

  \begin{scope}[on background layer]%
      \node [fit=(0)] (layer) {};%
  \end{scope}
  \begin{scope}[on background layer]%
      \node [fit=(4)] (layer) {};%
  \end{scope}
  \only<3-3>{\begin{scope}[on background layer]%
      \node [fit=(0), fill=green!50] (layer) {};%
  \end{scope}}
  \only<4-4>{\begin{scope}[on background layer]%
      \node [fit=(3), fill=green!50] (layer) {};%
  \end{scope}}
  \only<5-5>{\begin{scope}[on background layer]%
      \node [fit=(4), fill=green!50] (layer) {};%
  \end{scope}}
  \only<6-6>{\begin{scope}[on background layer]%
      \node [fit=(3), fill=green!50] (layer) {};%
  \end{scope}}
  \only<7-7>{\begin{scope}[on background layer]%
      \node [fit=(4), fill=green!50] (layer) {};%
  \end{scope}}

>>>>

  \draw[edge] (0) to node[very near start, above] (l0) {0} node[very near end, above] (e0) {1} (1);
  \draw[edge] (1) to node[very near start, below] (l1) {0} node[very near end, above] (e1) {1} (2);
  \draw[edge,bend right] (2.north west) to node[very near start, right] (l2) {0} node[very near end, above] (e2) {2} (0);
  \draw[edge] (0) to node[very near start, right] (l3) {1} node[very near end, left ] (e3) {0} (3);
  \draw[edge] (3) to node[very near start, above] {1} node[very near end, below] {1} (4);
  \draw[edge] (4) to node[very near start, below] {0} node[very near end, below] {1} (5);
  \draw[edge] (5) to node[very near start, above] {0} node[very near end, below] {2} (1);
  \draw[edge] (1) to node[very near start, left ] {3} node[very near end, left ] {2} (6);
  \draw[edge] (6) to node[very near start, above] {0} node[very near end, above] {1} (7);
  \draw[edge] (8) to node[very near start, above] {0} node[very near end, right] {0} (7);
  \draw[edge] (8) to node[very near start, above] {1} node[very near end, right] {2} (5);
  \draw[edge] (9) to node[very near start, below] {1} node[very near end, below] {3} (5);
  \draw[edge,bend right=20] (9) to node[very near start, below] {0} node[very near end, below] {1} (6);

  \begin{scope}[on background layer]%
      \node [fit=(0)] (layer) {};%
  \end{scope}
  \begin{scope}[on background layer]%
      \node [fit=(4)] (layer) {};%
  \end{scope}
  \only<3-3>{\begin{scope}[on background layer]%
      \node [fit=(0), fill=green!50] (layer) {};%
      \node [fit=(l0), fill=blue!50, inner sep=0pt] {};
  \end{scope}}
  \only<4-4>{\begin{scope}[on background layer]%
      \node [fit=(1), fill=green!50] (layer) {};%
      \node [fit=(l1), fill=blue!50, inner sep=0pt] {};
      \node [fit=(e0), fill=red!50, inner sep=0pt] {};
  \end{scope}}
  \only<5-5>{\begin{scope}[on background layer]%
      \node [fit=(2), fill=green!50] (layer) {};%
      \node [fit=(l2), fill=blue!50, inner sep=0pt] {};
      \node [fit=(e1), fill=red!50, inner sep=0pt] {};
  \end{scope}}
  \only<6-6>{\begin{scope}[on background layer]%
      \node [fit=(0), fill=green!50] (layer) {};%
      \node [fit=(l3), fill=blue!50, inner sep=0pt] {};
      \node [fit=(e2), fill=red!50, inner sep=0pt] {};
  \end{scope}}
  \only<7-7>{\begin{scope}[on background layer]%
      \node [fit=(3), fill=green!50] (layer) {};%
      \node [fit=(e3), fill=red!50, inner sep=0pt] {};
  \end{scope}}

### 2016-05-12 tikz/portex.tex
slides "done"

  \draw[edge] (m1) to node[very near start, above] {\textcolor{green}{0}} (e1);
  \draw[edge] (m1) to node[near start, left] {\textcolor{green}{2}} (e2);

  \draw[edge] (m2) to node[very near start, above] {\textcolor{green}{1}} (e3);
  \draw[edge] (m2) to node[near start, right] {\textcolor{green}{2}} (e4);

  \draw[edge] (m1) to node[very near start, below] {\textcolor{green}{1}} node[very near end, above] {\textcolor{green}{0}} (m2);
\end{tikzpicture}

>>>>

  \draw[edge] (m1) to node[very near start, above] {\textcolor{blue}{0}} (e1);
  \draw[edge] (m1) to node[near start, left] {\textcolor{blue}{2}} (e2);

  \draw[edge] (m2) to node[very near start, above] {\textcolor{blue}{1}} (e3);
  \draw[edge] (m2) to node[near start, right] {\textcolor{blue}{2}} (e4);

  \draw[edge] (m1) to node[very near start, below] {\textcolor{blue}{1}} node[very near end, above] {\textcolor{blue}{0}} (m2);
\end{tikzpicture}

### 2016-05-12 tikz/regsim.tex
slides "done"

  \uncover<3->{
    \node[node] (r11) [below = 6cm of m1] {$0$};
    \node[node] (r12) [above = 2cm of r11] {$1$};
    \node[node] (r13) [below = 2cm of r11] {$2$};

    \node[node] (l11) [below = 6cm of m3] {$0$};
    \node[node] (l12) [above = 2cm of l11] {$1$};
    \node[node] (l13) [below = 2cm of l11] {$2$};

    \node       (anker) [below = 6.5cm of m2] {};
    \node[node] (mid0) [above right = 1cm and 1cm of anker] {$0$};
    \node[node] (mid1) [below right = 1cm and 1cm of anker] {$1$};
    \node[node] (mid2) [below = 3cm of anker] {$2$};
    \node[node] (mid3) [below left = 1cm and 1cm of anker] {$3$};
    \node[node] (mid4) [above left = 1cm and 1cm of anker] {$4$};
    \node[node] (mid5) [above = 3cm of anker] {$5$};

>>>>

  \uncover<3->{
    \node[node] (r11) [below = 6cm of m1] {0};
    \node[node] (r12) [above = 2cm of r11] {1};
    \node[node] (r13) [below = 2cm of r11] {2};

    \node[node] (l11) [below = 6cm of m3] {0};
    \node[node] (l12) [above = 2cm of l11] {1};
    \node[node] (l13) [below = 2cm of l11] {2};

    \node       (anker) [below = 6.5cm of m2] {};
    \node[node] (mid0) [above right = 1cm and 1cm of anker] {0};
    \node[node] (mid1) [below right = 1cm and 1cm of anker] {1};
    \node[node] (mid2) [below = 3cm of anker] {2};
    \node[node] (mid3) [below left = 1cm and 1cm of anker] {3};
    \node[node] (mid4) [above left = 1cm and 1cm of anker] {4};
    \node[node] (mid5) [above = 3cm of anker] {5};
